---
title: SOK
subtitle: Yield Aggregators in DeFi
author: "Jiahua (Java) Xu, Ph.D."
date: 2022
classoption: aspectratio=169    
output:
  beamer_presentation:
    slide_level: 2
    theme: Dresden
    keep_tex: no
    toc: false
    incremental: false
    colortheme: beaver
    fonttheme: structurebold
    highlight: haddock
    pandoc_args: ["--syntax-definition=solidity.xml"]
    includes:
      in_header: diss-beamer.sty
  ioslides_presentation:
    logo: figure/ucllogo.svg
  slidy_presentation:
    footer: "Yield Aggregators in DeFi"
link-citations: yes
bibliography: YieldAggregators.bib
# suppress-bibliography: no
...

```{r echo=FALSE, warning=FALSE}
library(magrittr)
options(stringsAsFactors=FALSE)

knitr::opts_chunk$set(echo = FALSE, cache = TRUE, eval=FALSE)
```


```{r child = 'yieldaggregators.Rmd', eval=TRUE}
```


## Thank you!

**Contact**

\vspace{0.6cm}

Jiahua (Java) Xu

\vspace{0.4cm}

UCL Centre for Blockchain Technologies


66-72 Gower Street



\vspace{0.4cm}

jiahua.xu@ucl.ac.uk

## References {.allowframebreaks}
\small

\widowpenalties 1 0